SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-02 maintex.tex
added simulations to the previous works comparisons

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/nuc_sep.pdf}
\caption[]{$\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red), \citet{Li:2008} (Orange), \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple).  }
\label{fig:nuc_sep}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/nuc_sep.pdf}
\caption[]{(\textbf{Top}) $\Delta$log(SFR) over projected separation for this sample (Black), \citet{Ellison:2008} (Red),  \citet{Scudder:2012} (Blue), \citet{Patton:2013} (Green), and \citet{Bustamante:2020} (Purple). (\textbf{Bottom}) $\Delta$log(sSFR) over projected separation for this sample (Black), \citet{Li:2008} (Red), and \citet{Patton:2020} (Blue).  }
\label{fig:nuc_sep}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\citet{Moreno:2015} used {\sc Gadget}-3, a smoothed particle hydrodynamics code, to study the spatial extend of the star formation enhancement. The merger simulations showed that the star formation enhancement was largely concentrated in the centers (R $<$ 1 kpc) of the paired galaxies and that the off-nuclear regions (1 $<$ R $<$ 10 kpc) showed a suppression to the star formation. \citet{Moreno:2015} also found that star formation offsets in lower mass secondary galaxies (in mergers with stellar mass ratios of 2.5:1) have a stronger radial dependence with respect to the more massive primary companion. This is in good agreement with our work, we found that secondary companions show moderately higher levels of sSFR enhancement in their centers in comparison to primary companions at the same mass ratio. Further, the outskirts of the primary companions feature no enhancement or suppression to their sSFR while the secondary companions show a strong suppression to the sSFR at large radii.

The sSFR as a function of separation was studied with the cosmological hydrodynamical simulations of IllustrisTNG \citep{Patton:2020}. In Figure \ref{fig:nuc_sep} we show the $\Delta$log(sSFR) enhancements across 2D separation (projected separation) from the TNG300-1 simulation. \citet{Patton:2020} found a sSFR enhancement which is 1.8$\times$ that of the isolated controls within a separation of 15 kpc and is statistically significant out to a 2d separation of $\sim$250 kpc. This enhancement is $\sim$0.1 dex lower than ours; however, our sSFR enhancement shown in \ref{fig:nuc_sep} was extracted from a 0.5\reff\ aperture while \citet{Patton:2020} extracted the sSFR from a 50\% half-mass radius. This means that our extraction radius is effectively twice a small and is more restricted to the central burst of star formation.
